Copulas and their potential for ecology

### 2019-12-20 Paper.Rmd
changed the N in the statistic for independence to n

For bivariate datasets 
$(x_i,y_i)$ for $i=1,...,n$, model selection involved several steps. 
First, we produced normalized ranks 
$u_i$ and $v_i$ as in the Introduction. 
Second, we tested the independence of the $u_i$ and $v_i$
using the statistic $\sqrt{(9N(N-1))/(4N+10)}|\tau|$, where $\tau$
is Kendall's tau for the data. @Genest2007 argue that this statistic is approximately standard normally
distributed. We used the 
implementation of this test in `BiCopIndTest` in the `VineCopula` package
in R. We tested for independence because our model selection 
algorithms were ineffective if data could not 
be distinguished from independent data, 
since many copula families include the independent copula. 
If independence could be rejected ($0.05$ level), model 
selection proceeded. Third, we fit 16 bivariate copula families (see below) to the 
normalized ranks via maximum likelihood. The approach of fitting
copula families to normalized ranks was recommended 
by @Genest1995 and @Shih1995. Their estimator of copula
parameters, which we use, is consistent, asymptotically normal,
and fully efficient at indepencence [@Genest1995]. @Genest2007
recommend carrying out inferences of dependence structures (which was our
goal here) using normalized ranks.
We used the fitting implementation given in `BiCopEst` in `VineCopula`.
Fourth, we obtained AIC and BIC values and accompanying model weights 
$\text{AIC}_{\text{w}}$ and 
$\text{BIC}_{\text{w}}$ [@burnham2003_modelselection] for each fitted copula. 
`BiCopEst` also 
provided lower- and 
upper-tail dependence of the best-fitting member of each family. 
$\text{AIC}_{\text{w}}$ values were used to get
model-averaged lower- and upper-tail dependence values using standard model averaging 
formulas [@burnham2003_modelselection]; likewise for BIC.

>>>>

For bivariate datasets 
$(x_i,y_i)$ for $i=1,...,n$, model selection involved several steps. 
First, we produced normalized ranks 
$u_i$ and $v_i$ as in the Introduction. 
Second, we tested the independence of the $u_i$ and $v_i$
using the statistic $\sqrt{(9n(n-1))/(4n+10)}|\tau|$, where $\tau$
is Kendall's tau for the data. @Genest2007 argue that this statistic is approximately standard normally
distributed. We used the 
implementation of this test in `BiCopIndTest` in the `VineCopula` package
in R. We tested for independence because our model selection 
algorithms were ineffective if data could not 
be distinguished from independent data, 
since many copula families include the independent copula. 
If independence could be rejected ($0.05$ level), model 
selection proceeded. Third, we fit 16 bivariate copula families (see below) to the 
normalized ranks via maximum likelihood. The approach of fitting
copula families to normalized ranks was recommended 
by @Genest1995 and @Shih1995. Their estimator of copula
parameters, which we use, is consistent, asymptotically normal,
and fully efficient at indepencence [@Genest1995]. @Genest2007
recommend carrying out inferences of dependence structures (which was our
goal here) using normalized ranks.
We used the fitting implementation given in `BiCopEst` in `VineCopula`.
Fourth, we obtained AIC and BIC values and accompanying model weights 
$\text{AIC}_{\text{w}}$ and 
$\text{BIC}_{\text{w}}$ [@burnham2003_modelselection] for each fitted copula. 
`BiCopEst` also 
provided lower- and 
upper-tail dependence of the best-fitting member of each family. 
$\text{AIC}_{\text{w}}$ values were used to get
model-averaged lower- and upper-tail dependence values using standard model averaging 
formulas [@burnham2003_modelselection]; likewise for BIC.
